### 2017-02-28 Hhh/Hhh.tex
A few more minor changes before sending off to supervisors

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_010-a.pdf}
\caption[The expected and observed upper limits at the 95 \% CL on the 
\xsbr for the \AtoZhtolltautau process.]{The expected (dashed) and observed (solid)
upper limits at the 95\% \ac{CL} on the \xsbr for the \AtoZhtolltautau process.
The green and yellow bands indicate the $\pm 1 \sigma $ and $\pm 2\sigma$
expectations \cite{CMS-HIG-14-034}.}
\label{fig:AZhUpperLimits}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_008-d.pdf}}
\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/hhh_limit_comparison.pdf}}
\caption[Expected and observed upper limits at the 95\% CL on 
\xsbr for the \Htohhtobbtautau process.]{Expected and observed upper limits at the 95\% \ac{CL} on \xsbr  
for the \Htohhtobbtautau process. In (a) the three final states of \etau, \mutau and \tautau are combined \cite{CMS-HIG-14-034}.
(b) Shows the expected upper limits at the 95\% \ac{CL} on \xsbr for the \Htohhtobbtautau
process, separated by channel. The blue line shows the limit for the \tautau channel, the green line for the \mutau channel, the red line
for the \etau channel and the black line the limit for all three channels combined. Up to around \mH~$= 320\,\GeV$ the \mutau channel is the most
sensitive, with the \tautau channel being more sensitive at higher masses.}
\label{fig:hhh_results_modelindep}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[type-II 2HDM]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_012.pdf}}
\subfloat[low-\tanb~MSSM scenario]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_011.pdf}}
\caption[Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
interpreted in a type-II 2HDM and in the low-\tanb~MSSM scenario.]{Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
interpreted in (a) a type-II \ac{2HDM} assuming $m_{\PHiggs} = m_{\PHiggsps} = m_{\PHiggs^{+}} = 300\,\GeV$ and 
(b) in the low-\tanb~MSSM scenario. The shaded blue area bounded by
the solid black line indicates the observed excluded region at 95\% \ac{CL}.
The dashed black line indicates the expected exclusion, with the grey bands showing
the $\pm 1\sigma$ and $\pm2\sigma$ expected exclusion \cite{CMS-HIG-14-034}. The area
bounded by the red line is the region of phase space where \mh~$\neq 125 \pm 3\,\GeV$
 and is therefore excluded.}
\label{fig:HhhAZhMSSM2HDM}
\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_010-a.pdf}
\caption[The expected and observed upper limits at the 95 \% CL on the 
\xsbr for the \AtoZhtolltautau process.]{The expected (dashed) and observed (solid)
upper limits at the 95\% \ac{CL} on the \xsbr for the \AtoZhtolltautau process.
The green and yellow bands indicate the $\pm 1 \sigma $ and $\pm 2\sigma$ 
probability intervals on the expected limit \cite{CMS-HIG-14-034}.}
\label{fig:AZhUpperLimits}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_008-d.pdf}}
\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/hhh_limit_comparison.pdf}}
\caption[Expected and observed upper limits at the 95\% CL on 
\xsbr for the \Htohhtobbtautau process.]{Expected and observed upper limits at the 95\% \ac{CL} on \xsbr  
for the \Htohhtobbtautau process. In (a) the three final states of \etau, \mutau and \tautau are combined. The green and yellow bands indicate the $\pm 1 \sigma $ and $\pm 2\sigma$ 
probability intervals on the expected limit  \cite{CMS-HIG-14-034}.
(b) Shows the expected upper limits at the 95\% \ac{CL} on \xsbr for the \Htohhtobbtautau
process, separated by channel. The blue line shows the limit for the \tautau channel, the green line for the \mutau channel, the red line
for the \etau channel and the black line the limit for all three channels combined. Up to around \mH~$= 320\,\GeV$ the \mutau channel is the most
sensitive, with the \tautau channel being more sensitive at higher masses.}
\label{fig:hhh_results_modelindep}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[type-II 2HDM]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_012.pdf}}
\subfloat[low-\tanb~MSSM scenario]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_011.pdf}}
\caption[Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
interpreted in a type-II 2HDM and in the low-\tanb~MSSM scenario.]{Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
interpreted in (a) a type-II \ac{2HDM} assuming $m_{\PHiggs} = m_{\PHiggsps} = m_{\PHiggs^{+}} = 300\,\GeV$ and 
(b) in the low-\tanb~MSSM scenario. The shaded blue area bounded by
the solid black line indicates the observed excluded region at 95\% \ac{CL}.
The dashed black line indicates the expected exclusion, with the grey bands showing
the $\pm 1\sigma$ and $\pm2\sigma$ probability intervals on the expected exclusion \cite{CMS-HIG-14-034}. The area
bounded by the red line is the region of phase space where \mh~$\neq 125 \pm 3\,\GeV$
 and is therefore excluded.}
\label{fig:HhhAZhMSSM2HDM}
\end{center}
\end{figure}

### 2017-02-28 MSSM/MSSM.tex
A few more minor changes before sending off to supervisors

Because the analysis targets these two signal processes, it is possible
to redefine the likelihood as a function of both the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ signals:
\begin{equation}\label{mssm_2D_likelihood}
\mathcal{L}(\text{data}|\mu_{\Pg\Pg\phi},\mu_{\Pbottom\Pbottom\phi}, \theta) = \mathcal{L}(\text{data}|\mu_{\Pg\Pg\phi} \cdot s_{\Pg\Pg\phi}(\theta) + \mu_{\Pbottom\Pbottom\phi}\cdot s_{\Pbottom\Pbottom\phi}(\theta) + b(\theta)),
\end{equation}
where $s_{\Pg\Pg\phi}$ and $s_{\Pbottom\Pbottom\phi}$ are the signal expectations of the two
production processes and the signal strength modifiers $\mu_{\Pg\Pg\phi}$ and $\mu_{\Pbottom\Pbottom\phi}$ now represent the \xsbr of the
two processes. Using this definition a likelihood scan in two dimensions can be performed.
First a 2D grid in $\mu_{\Pg\Pg\phi}$ and $\mu_{\Pbottom\Pbottom\phi}$, both required to be greater than or equal to zero, is constructed. 
The negative log-likelihood,
\begin{equation}\label{eqn:nll}
\text{NLL} = -\text{ln }\mathcal{L}(\text{data}|\mu_{gg\phi},\mu_{bb\phi},\theta),
\end{equation}
is then evaluated at each point. The point in the 2D grid where the NLL reaches
its lowest value gives the best fit values for $\mu_{\Pg\Pg\phi}$ and $\mu_{\Pbottom\Pbottom\phi}$. The
68\% and 95\% confidence level regions are constructed as the values
$\mu_{\Pg\Pg\phi}^{N\%}$ and $\mu_{\Pbottom\Pbottom\phi}^{N\%}$ for which:
\begin{equation}\label{eqn:mssm_2D_deltaNLL}
\begin{split}
\Delta(\text{NLL})_{68\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{\Pg\Pg\phi}^{68\%},\mu_{\Pbottom\Pbottom\phi}^{68\%}) = 1.14, ~\\
\Delta(\text{NLL})_{95\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{\Pg\Pg\phi}^{95\%},\mu_{\Pbottom\Pbottom\phi}^{95\%}) = 3.00.
\end{split}
\end{equation}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.65\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-a.pdf}}~\\
\subfloat[hMSSM scenario]{\includegraphics[width=0.65\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-b.pdf}}
\end{center}
\caption[Exclusions in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the hMSSM
scenario of the \AHtotautau analysis.]{Exclusions in (a) the $m_{\PHiggslight}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
obtained by the combination
of all channels. The blue shaded area bounded by the 
solid black line is the observed exclusion, with the dashed black line the
expected exclusion. The light and dark grey bands indicate
the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected exclusion in the \ac{SM} hypothesis.
The red shaded area in the $m_{\PHiggslight}^{\text{mod}+}$ figure
is excluded by the lack of a light Higgs boson with mass compatible with $125\,\GeV$ in the model \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_mhmodp_2016}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.6\textwidth]{./MSSM/Figures/mssm_combination_mhmodp_cmb.pdf}}~\\
\subfloat[hMSSM scenario]{\includegraphics[width=0.6\textwidth]{./MSSM/Figures/mssm_combination_hMSSM_cmb.pdf}}
\end{center}
\caption[Exclusions in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the hMSSM
scenario of the combination of the 2015 and 2016 \AHtotautau analyses.]{Exclusions in (a) the $m_{\PHiggslight}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
obtained by the combination
of all channels of the 2015 and 2016 \AHtotautau analyses. The blue shaded area bounded by the 
solid black line is the observed exclusion, with the dashed black line the
expected exclusion. The light and dark grey bands indicate
the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected exclusion in the \ac{SM} hypothesis.
The red shaded area in the $m_{\PHiggslight}^{\text{mod}+}$ figure
is excluded by the lack of a light Higgs boson with mass compatible with $125\,\GeV$ in the model. The dashed (solid)
blue lines indicate the expected (observed) exclusion from the 2016 analysis alone.}
\label{fig:mssm_mhmodp_20152016}
\end{figure}

>>>>

Because the analysis targets these two signal processes, it is possible
to redefine the likelihood as a function of both the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ signals:
\begin{equation}\label{mssm_2D_likelihood}
\mathcal{L}(\text{data}|\mu_{\Pg\Pg\phi},\mu_{\Pbottom\Pbottom\phi}, \theta) = \mathcal{L}(\text{data}|\mu_{\Pg\Pg\phi} \cdot s_{\Pg\Pg\phi}(\theta) + \mu_{\Pbottom\Pbottom\phi}\cdot s_{\Pbottom\Pbottom\phi}(\theta) + b(\theta)),
\end{equation}
where $s_{\Pg\Pg\phi}$ and $s_{\Pbottom\Pbottom\phi}$ are the signal expectations of the two
production processes and the signal strength modifiers $\mu_{\Pg\Pg\phi}$ and $\mu_{\Pbottom\Pbottom\phi}$ now represent the \xsbr of the
two processes. Using this definition a likelihood scan in two dimensions can be performed.
First a 2D grid in $\mu_{\Pg\Pg\phi}$ and $\mu_{\Pbottom\Pbottom\phi}$, both required to be greater than or equal to zero, is constructed. 
The negative log-likelihood,
\begin{equation}\label{eqn:nll}
\text{NLL} = -\text{ln }\mathcal{L}(\text{data}|\mu_{gg\phi},\mu_{bb\phi},\theta),
\end{equation}
is then evaluated at each point. The point in the 2D grid where the NLL reaches
its lowest value gives the best fit values for $\mu_{\Pg\Pg\phi}$ and $\mu_{\Pbottom\Pbottom\phi}$. The
68\% and 95\% confidence level regions are constructed as the values
$\mu_{\Pg\Pg\phi}^{N\%}$ and $\mu_{\Pbottom\Pbottom\phi}^{N\%}$ for which:
\begin{equation}\label{eqn:mssm_2D_deltaNLL}
\begin{split}
\Delta(\text{NLL})_{68\%} &= \text{NLL}(\mu_{\Pg\Pg\phi}^{68\%},\mu_{\Pbottom\Pbottom\phi}^{68\%}) - \text{NLL}(\text{best fit}) = 1.14, ~\\
\Delta(\text{NLL})_{95\%} &= \text{NLL}(\mu_{\Pg\Pg\phi}^{95\%},\mu_{\Pbottom\Pbottom\phi}^{95\%}) - \text{NLL}(\text{best fit}) = 3.00.
\end{split}
\end{equation}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.65\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-a.pdf}}~\\
\subfloat[hMSSM scenario]{\includegraphics[width=0.65\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-b.pdf}}
\end{center}
\caption[Exclusions in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the hMSSM
scenario of the \AHtotautau analysis.]{Exclusions in (a) the $m_{\PHiggslight}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
obtained by the combination
of all channels. The blue shaded area bounded by the 
solid black line is the observed exclusion, with the dashed black line the
expected exclusion. The light and dark grey bands indicate
the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected exclusion under the \ac{SM} hypothesis.
The red shaded area in the $m_{\PHiggslight}^{\text{mod}+}$ figure
is excluded by the lack of a light Higgs boson with mass compatible with $125\,\GeV$ in the model \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_mhmodp_2016}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.6\textwidth]{./MSSM/Figures/mssm_combination_mhmodp_cmb.pdf}}~\\
\subfloat[hMSSM scenario]{\includegraphics[width=0.6\textwidth]{./MSSM/Figures/mssm_combination_hMSSM_cmb.pdf}}
\end{center}
\caption[Exclusions in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the hMSSM
scenario of the combination of the 2015 and 2016 \AHtotautau analyses.]{Exclusions in (a) the $m_{\PHiggslight}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
obtained by the combination
of all channels of the 2015 and 2016 \AHtotautau analyses. The blue shaded area bounded by the 
solid black line is the observed exclusion, with the dashed black line the
expected exclusion. The light and dark grey bands indicate
the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected exclusion under the \ac{SM} hypothesis.
The red shaded area in the $m_{\PHiggslight}^{\text{mod}+}$ figure
is excluded by the lack of a light Higgs boson with mass compatible with $125\,\GeV$ in the model. The dashed (solid)
blue lines indicate the expected (observed) exclusion from the 2016 analysis alone.}
\label{fig:mssm_mhmodp_20152016}
\end{figure}
